Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-22 paper.qmd
Find the best model with UMAP and update the video link

![](figures/scurve/sc_1.png)

![](figures/scurve/sc_2.png)

![](figures/scurve/sc_3.png)

Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data ($(s_1, \ s_2) = (-0.160, \ -0.263)$, $b = 405 \  (15, \ 27)$, $m = 70$, benchmark value to remove low density hexagons is $0.250$, and benchmark value to remove large edges is $0.159$). MSE is $0.0462$. The model closely fits the shape, but it doesn't fully fill out the width of the S, which means that it does not adequately capture the surface (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>).
:::

>>>>

![](figures/scurve/sc_umap_best_1.png)

![](figures/scurve/sc_umap_best_2.png)

![](figures/scurve/sc_umap_best_3.png)

Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data ($(s_1, \ s_2) = (-0.160, \ -0.263)$, $b = 405 \  (15, \ 27)$, $m = 70$, benchmark value to remove low density hexagons is $0.250$, and benchmark value to remove large edges is $0.159$). MSE is $0.0462$. The model closely fits the shape, but it doesn't fully fill out the width of the S, which means that it does not adequately capture the surface (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/i7F7xpN1Hz8>).
:::
